---
title: "W201 Portfolio"
author: "Nicholas McCormack"
date: "MIDS Fall 2017"
site: bookdown::bookdown_site
documentclass: book
---

<!-- This won't be displayed but it will initialize your R session. Add any R libraries you need here. -->
```{r init,include=FALSE,echo=FALSE}
library(magrittr)
```


# Welcome! {-}

This portfolio consists of two ideas for data science projects that I came up with for the w201 course, in the MIDS program, at UC-Berkeley. The first project, Tinker, is an app that analyzes data collected from sensors on a golfer's body to deliver actionable swing changes that the golfer can make to improve his or her power, accuracy, and consistency. It aims to revolutionize the way golfers train and to shake up the coaching space. The second idea, Tit-For-Tat, is an online community, based on a barter-economic model, where local individuals are connected based on shared needs for services. The goal is to maximize what we can get done in a day since our free-time is not uniformly distributed. 

<!-- Below this line is just examples of how you can embed video from Google Drive. First you have to enable sharing, then just get the object ID which is that long string between d/ and /preview and will also be appended to any sharing link you generate for your video. -->
<p>
```{r Tinker-Presentation,echo=FALSE,fig.cap='Video Presentation for First Big Idea!',fig.align='center'}
knitr::include_url('https://drive.google.com/open?id=1wwDnSPHrCGcDv7iIKA1SNrbw6SBRThzV')
```

### Abstract of my first cool idea
Everyone has things they better at than others, chores they find more enjoyable than others, and days when there just isn't enough time to take care of all of life's responsibilities. Getting the help or services we need, when we need them, can be incredibly expensive; however, the alternative to outsourcing some of these tasks is oftentimes just as costly in time and energy spent. Tit For Tat is an online marketplace aimed at solving this dilemma. Our goal is to connect people who need services with people who are able to supply them. The catch? No currency is exchanged between the two parties.

To accomplish this, Tit For Tat matches the needs and offered services of Client *A* with the needs and offered services of Client *B*. When a match is found, Client *A* exchanges his/her services on days $y_1$..$y_n$ with the needs of Client *B* on days $z_1$..$z_n$. Free time is maximized for both parties; everyone benefits from the system.

### Abstract of my second cool idea {-}

Every year, millions of amateur golfer spend countless hours tinkering with their swings. Despite all of this tinkering, many of these individuals will spend the majority of their time with little or no knowledge about what they need to fix or how to go about fixing what they have identified as the problem. Professional lessons are expensive, and coaching ceases when the lesson ends.  

At Tinker, we want to revolutionize the coaching space for the sport of golf. By utilizing strategically placed sensors in the golfer's wrists, elbows, shoulders, knees, and ankles (as well as information about the shot's outcome, tendancies of the golfer, and his/her swing type), we are able to provide a service where golfers of all swing types and skill levels get actionable tips and solutions, whenever they want to play, for a fraction of the cost of traditional lessons. Tinker makes those countless hours practicing start to count; we want to do the tinkering for you.
  

## About the author {-}

I'm Nick McCormack, and I currently work as a business intelligence analyst at Milwaukee Tool. In a previous life, I was a Ph.D. candidate in cognitive psychology/neuroscience at Ohio State after getting my undergraduate degree in psychology from Marquette University. I have experience working both independently and as part of a team on research and programming projects, with large data sets, and with sensitive information. In my free time, I like spending time with my friends, my family, and my dog, LeBron (who is half-Cavalier). I love playing and following sports, running, and music. A personal goal of mine is to one day work in basketball analytics for an NBA team.

*Updated: `r Sys.Date()`*
